A sensor grid approach for large scale acoustic monitoring

### 2017-08-22 paper/article.tex
Paper corrections
more inputs

%% \linenumbers
\clearpage
%% main text
\section{Introduction}
%\label{}
\pa{
// Beaucoup de fomer/latter
// Le terme soundscape inclut la perception de lenvironnment sonore. Si tu veux parler juste de lenvironnement sonore "urban sound environment" est plus approprie.
// Ref Judi: Picaut, Judicaël, Arnaud Can, Jérémy Ardouin, Pierre Crépeaux, Thierry Dhorne, David Écotière, Mathieu Lagrange, et al. « Characterization of urban sound environments using a comprehensive approach combining open data, measurements, and modeling ». In The Journal of the Acoustical Society of America, 141:3808-3808. Boston, USA: Acoustical Society of America, 2017. doi:10.1121/1.4988416.
}
The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc\footnote{\url{htttp://wp.nyu.edu/sonyc}} \cite{mydlarz2017implementation} and cense\footnote{\url{htttp://cense.ifsttar.fr}} \pa{ref papier de judicael ?} \cite{} projects.

@@

The data of interest is first acoustic indicators (LAeq, ...) and second the presence of sound sources of interest (bird calls, sirens, ...). The latter allows us to better assess soundscapes in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017modeling}. This detection step can respectively be operated online (on the sensors) or offline (on the data servers).

The former is efficient in terms of data storage as only the detection events are transmitted and is thus currently considered in several approaches \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}. Though, it requires the availability of computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware do not allow them to be autonomous using power sources like decent size solar panels. Furthermore, the detection is done once and cannot be recomputed during posterior analyses.

The latter scheme has several benefits. First, the sensor task is much simpler and can thus be implemented using low consumption processors, potentially being autonomous in terms of energy. This will ease the deployment of the network. Second, it allows researchers to gather large amount of data that can be post processed and studied further offline. Data can be re analyzed following newer classification schemes or using new indicators.

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figures/censeCoder}
\vspace{-0.15in}
\caption{Alternative implementations of the sensor grid approach for the monitoring of the acoustic environment. In A) the raw audio is transmitted, in B) only the detected events, and in C) a compressed spectral representation. Thickness of arrows roughly indicate bandwidth and thickness of boxes roughly indicates the level of computation or storage required.\pa{Figure non appelee}}
\label{fig:codingScheme}
\end{figure}

@@

Even though the above discussed indicators provide more richness than $L_{eq}$, studies show that abstract statistics are still not sufficient to fully model the soundscapes \pa{refs}. The recognition of sources of interest is thus of importance. As far as the encoding scheme is concerned, it is thus important that the encoded data allows us to compute the above cited indicators but also to allow us to recognize the sources of interest with state of the art methods.

@@

An audio encoding scheme has been described and motivated for use in a sensor grid approach to tackle the problem of large scale acoustic monitoring.

The proposed approach has the following benefits:
\begin{itemize}
	\item precision: the impact of the quantization step for 8 bits codewords is found to be very small (< 0.5dB) and thus:
	- respect the acoustics indicators which could be calculated from the spectrogram.
	- permits to perform the sound recognition with the same quality than directly from the spectrogram.
	\item efficiency: for fast and slow modes, the bitrate is respectively about 1.4~kbps and 0.4~kbps for the high precision mode
	\item privacy: at all operating modes, the reverted audio signal is found to be inintelligible.
\end{itemize}

@@

Future work will study the usefulness of more sophisticated encoding paradigms in order to further improve bitrate efficiency and a more thorough investigation on the inversion methods in order to ensure that the inintelligibility constraint is indeed not violated for fast settings.

>>>>

%% \linenumbers
\clearpage
%% main text
\section{Introduction}
%\label{}

The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc\footnote{\url{htttp://wp.nyu.edu/sonyc}} \cite{mydlarz2017implementation} and cense\footnote{\url{htttp://cense.ifsttar.fr}} \cite{picault2017} projects.

@@

The data of interest is first acoustic indicators (LAeq, ...) and second the presence of sound sources of interest (bird calls, sirens, ...). The latter allows us to better assess the human perception of the urban sound environment in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017modeling}. This detection step can respectively be operated online (on the sensors) or offline (on the data servers) leading to different grid designs, see Figure \ref{fig:codingScheme}.

Online detection is efficient in terms of data storage as only the detection events are transmitted and is thus currently considered in several approaches \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}. Though, it requires the availability of computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware do not allow them to be autonomous using power sources like decent size solar panels. Furthermore, the detection is done once and cannot be recomputed during posterior analyses.

The alternative scheme has several benefits. First, the sensor task is much simpler and can thus be implemented on low energy consumption processors, potentially being autonomous in terms of energy. This will ease the deployment of the network. Second, it allows researchers to gather large amount of data that can be post processed and studied further offline. Data can be re analyzed following newer classification schemes or using new indicators.

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figures/censeCoder}
\vspace{-0.15in}
\caption{Alternative implementations of the sensor grid approach for the monitoring of the acoustic environment. In A) the raw audio is transmitted, in B) only the detected events, and in C) a compressed spectral representation. Thickness of arrows roughly indicate bandwidth and thickness of boxes roughly indicates the level of computation or storage required.}
\label{fig:codingScheme}
\end{figure}

@@

Even though the above discussed indicators provide more richness than $L_{eq}$, studies show that abstract statistics are still not sufficient to fully model the soundscapes \pa{refs} \cl{can you add some ?}. The recognition of sources of interest is thus of importance. As far as the encoding scheme is concerned, it is thus important that the encoded data allows us to compute the above cited indicators but also to allow us to recognize the sources of interest with state of the art methods.

@@

An audio encoding scheme has been described and motivated for use in a sensor grid approach to tackle the problem of large scale acoustic monitoring. It has been designed to transfer data from acoustic sensors to processing and storage servers in an efficient and effective manner. It relies on a lossy audio coding scheme designed to the ensure privacy of citizens while retaining the needed amount of acoustic precision to compute standard acoustic descriptors and to allow the recognition of events of interest at a state of the art level of recognition accuracy.

It is based on a third octave spectral representation computed at an adjustable frame rate, encoded using an Huffman encoding scheme after logarithmic compression and differential encoding.

The proposed approach has the following benefits:
\begin{itemize}
	\item precision: the impact of the quantization step for 8 bits codewords is found to be very small (< 0.5dB) and thus:
	- do not impact the quality of the acoustics indicators.
	- permits to perform the sound recognition with the same quality than directly from the spectrogram.
	\item efficiency: for fast and slow modes, the bitrate is respectively about 1.4~kbps and 0.4~kbps for the high precision mode
	\item privacy: at all operating modes, the reverted audio signal is found to be inintelligible according to a perceputal test.
\end{itemize}

The encoding scheme is designed to be simple to use and to lead to an efficient data format for storage and sharing acroos the research community. To encourage its use for other research projects, an open source Matlab implementation of the coder is available.

@@

Future work will focus on the use of such a sensor grid approach as part of the cense project where its effectiveness will be assessed in filed conditions. The usefulness of more sophisticated encoding paradigms in order to further improve bitrate efficiency should also be studied. Also, a more thorough investigation shall be performed on the inversion methods used to recover audio data from encoded data in order to ensure that the inintelligibility constraint is indeed not violated for fast settings.
